Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-10 main.tex

Many strategies can be represented by multiple archetypes, however some
archetypes will be more efficient in encoded the patterns present in the data.
The fact that the Lookerup strategy does the best for the standard
tournament indicates that it represents an efficient reduction of
dimension which in turn makes its training more efficient. In particular the
first rounds of play were valuable bit of information. For the noisy
tournament however the dimension reduction represented by some archetypes
indicates that some features of the data are not captured by the lookup
tables while they are by the neural network and the finite state machine,
allowing them to adapt better to the noisy environment. Intuitively, a noisy
environment can significantly affect a lookup table based on the last two rounds
of play since these action pairs compete with probing defections, apologies, and
retaliations. Accordingly, it is not surprising that additional parameter space
is needed to adapt to a noisy environment.

>>>>

Many strategies can be represented by multiple archetypes, however some
archetypes will be more efficient in encoding the patterns present in the data.
The fact that the Lookerup strategy does the best for the standard
tournament indicates that it represents an efficient reduction of
dimension which in turn makes its training more efficient. In particular the
first rounds of play were valuable bit of information. For the noisy
tournament however the dimension reduction represented by some archetypes
indicates that some features of the data are not captured by the lookup
tables while they are by the neural network and the finite state machine,
allowing them to adapt better to the noisy environment. Intuitively, a noisy
environment can significantly affect a lookup table based on the last two rounds
of play since these action pairs compete with probing defections, apologies, and
retaliations. Accordingly, it is not surprising that additional parameter space
is needed to adapt to a noisy environment.
